The 2014 SMT Competition

### 2015-07-28 2014/report/SMTCOMP.tex
typo
timeout discussion for application track

For comparison, the previous computational cluster (SMT-Exec) had just 11 nodes:
\begin{itemize}
\item Nine are 2.4\,GHz AMD Opteron 250s, configured for single core, 64-bit processing, 1 MB cache, 4 GB main memory
\item Two are 2.53\,GHz Intel Xeon E5540s, configured for single core, 64-bit processing, 8 MB cache, 12 GB main memory
\end{itemize}
All eleven execution nodes have the same software configuration:
\begin{itemize}
\item Linux, kernel version 2.6.18-128.2.1.el5
\item Red Hat Enterprise Linux Client release 5.2 (Tikanga)
\item glibc-2.5-24.el5_2.2
\item runtime libraries from gcc-4.1.2-42.el5
\end{itemize}
The raw CPU speed is not significantly different, but memory size, number of cores, and number of nodes is greatly increased.

@@

>>>>

For comparison, the previous computational cluster (SMT-Exec) had just 11 nodes:
\begin{itemize}
\item Nine are 2.4\,GHz AMD Opteron 250s, configured for single core, 64-bit processing, 1 MB cache, 4 GB main memory
\item Two are 2.53\,GHz Intel Xeon E5540s, configured for single core, 64-bit processing, 8 MB cache, 12 GB main memory
\end{itemize}
All eleven execution nodes have the same software configuration:
\begin{itemize}
\item Linux, kernel version 2.6.18-128.2.1.el5
\item Red Hat Enterprise Linux Client release 5.2 (Tikanga)
\item glibc-2.5-24.el5\_2.2
\item runtime libraries from gcc-4.1.2-42.el5
\end{itemize}
The raw CPU speed is not significantly different, but memory size, number of cores, and number of nodes is greatly increased.

@@

We can also consider the effect of the choice of timeout on the application track. This effect is more complicated than for the main track since an application track benchmark can have partial results. For example, if a benchmark contains 100 check-sat commands, a solver may report correct answers on 0 to 100 of them prior to timing out. Furthermore the seven divisions that have results show very different characteristics. In four of the divisions (QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, UFLRA) over 90\% of the solver-benchmarks jobs were completed before the timeout; for QF\_UFLRA it was over 99\%. The other three divisions had much harder benchmarks. For example, for QF\_BF, only 1\% of solver-benchmark pairs were completely solved by 1 second and only 42\% by the timeout.  These three divisions also have many fewer benchmarks---a few hundred, rather than several thousand. Changing the timeouts further might affect the results of these divisions significantly, but not those of the four divisions with many more benchmarks.
